\sectionTitle{Experience}{}

\begin{experiences}
    \researchexperience
    {Aug. 2022}   {LINE Corporation | Research Intern{\normalfont  ~ [\href{https://linecorp.com/en/}{\small{\websiteSymbol}}]}}{Tokyo, Japan}{Tokyo, Japan}
    {Sep. 2022} {\textit{Advisor: Mr. Masayoshi Kondo and \href{https://scholar.google.co.jp/citations?user=VVoeVYIAAAAJ}{Dr. Yoshihisa Ijiri}}\\
    Worked on establishing a new technology for automatic generation of advertising videos using images.
    }

    \emptySeparator
    \researchexperience
    {Aug. 2021}   {NTT Human Informatics Laboratories | Research Intern{\normalfont  ~ [\href{https://www.rd.ntt/e/hil/}{\small{\websiteSymbol}}]}}{Kanagawa, Japan}{Kanagawa, Japan}
    {Sep. 2021} {\textit{Advisor: \href{https://www.knishida.info/}{Dr. Kyosuke Nishida}}\\
    Worked on establishing a new pre-training method for document image understanding.
    }

    \emptySeparator
    \researchexperience
    {Dec. 2022}   {CyberAgent Inc. | Collaborative Researcher{\normalfont  ~ [\href{https://www.cyberagent.co.jp/news/detail/id=26231}{\small{\websiteSymbol}}]}}{Tokyo, Japan}{Tokyo, Japan}
    {Jul. 2021} {\textit{Advisors: \href{https://mayu-ot.github.io/}{Dr. Mayu Otani}, \href{https://naoto0804.github.io/}{Dr. Naoto Inoue}, {Mr. Yuki Iwazaki}}\\
    Working on establishing multi-modal deep learning model for ad creative understanding in \href{https://www.cyberagent.co.jp/news/detail/id=26231}{a special research position for doctoral students adopted as JSPS Research fellow (DC1, DC2, PD)}.
    \vskip 0.1cm
    }
    \researchexperience
    {}   {}{}{}
    {May. 2019} {\textit{Research Intern | Advisor: {Mr. Yuki Iwazaki}}\\
    Investigated fundamental research to evaluate and analyze ad creatives and its landing pages, presented at academic symposium in Japan.
    }

    \emptySeparator
    \researchexperience
    {Mar. 2021}   {AppBrew Inc. | AI x Ad Consultant{\normalfont  ~ [\href{https://appbrew.io/}{\small{\websiteSymbol}}]}}{Tokyo, Japan}{Tokyo, Japan}
    {Feb. 2021} {
    \begin{itemize}
        \item Surveyed methods for automatically creating/generating ad creatives.
        \item Advised on the improvement of advertising creative creation methods.
        \item Wrote an article about AI x Adtech in Japanese:
    \end{itemize}
    }

    \emptySeparator
    \researchexperience
    {Aug. 2020}   {Tokyo Women's Medical University | Part-time Job{\normalfont  ~ [\href{https://www.twmu.ac.jp/english/}{\small{\websiteSymbol}}]}}{Tokyo, Japan}{Tokyo, Japan}
    {Jul. 2020} {
    \textit{Advisors: \href{https://www.researchgate.net/scientific-contributions/Masaru-Tanaka-2078765174}{Prof. Masaru Tanaka}, \href{https://researchmap.jp/7000025183?lang=en}{Dr. Noriko Umegaki}, \href{https://scholar.google.com/citations?user=ghyQxvIAAAAJ}{Prof. Hitoshi Iyatomi}}\\
    Assisted in collecting skin images for the construction of an automated diagnostic system.

    }

    \emptySeparator
    \researchexperience
    {Jul. 2019}   {M3 Inc. | Software Engineer Intern{\normalfont  ~ [\href{https://corporate.m3.com/en/}{\small{\websiteSymbol}}]}}{Tokyo, Japan}{Tokyo, Japan}
    {Jun. 2019} {
    \begin{itemize}
        \item Worked on quantifying and visualizing doctors' interest from browsing history.
        \item Built a system for recommending articles for doctors based on the analysis from scratch
    \end{itemize}
    }

    \emptySeparator
    \researchexperience
    {Aug. 2018}   {Piascore Inc. | Deep Learning Advisor{\normalfont  ~ [\href{http://piascore.com/en/}{\small{\websiteSymbol}}]}}{Tokyo, Japan}{Tokyo, Japan}
    {Jun. 2018} {
    Advised how to solve practical problems of existing services that use machine learning algorithms and deep learning models, showing examples of the kind of problems recent deep learning models are capable of solving.
    }

    \emptySeparator
    \researchexperience
    {Present}   {Gunosy Inc. | Research Intern{\normalfont  ~ [\href{https://gunosy.co.jp/en/}{\small{\websiteSymbol}}]}}{Tokyo, Japan}{Tokyo, Japan}
    {Aug. 2018} {\textit{Advisor: Dr. Yoshifumi Seki}\\
    Worked on fundamental research to evaluate and analyze ad creatives, resulting in a presentation at Applied Science track of KDD, a top data mining conference.
    \vskip 0.1cm
    }
    \researchexperience
    {Jul. 2018}   {}{}{}
    {Mar. 2017} {\textit{Software Engineer Intern}\\
        Worked on (1) improving the user experience and participated in improving the logic of the article distribution, and (2) analyzing log data through visualization of multiple KPIs and contributing to the growth of the service.
    }

    \emptySeparator
    \researchexperience
    {}   {FarberCompany Inc. | Software Engineer Intern{\normalfont  ~ [\href{https://www.fabercompany.co.jp/}{\small{\websiteSymbol}}]}}{Tokyo, Japan}{Tokyo, Japan}
    {Mar. 2018} {
    Implemented machine learning models that accurately capture semantic features of a document in a document similarity (Engineer internship 3days / ¥100,000).
    }

    \emptySeparator
    \researchexperience
    {Apr. 2021}   {NVIDIA Japan | Teaching Assistant for Deep Learning Hands-On Training Lab{\normalfont  ~ [\href{https://www.nvidia.com/ja-jp/}{\small{\websiteSymbol}}]}}{Tokyo, Japan}{Tokyo, Japan}
    {Jan. 2016} {
    Assisted in several workshops in Tokyo relating to deep learning and CUDA:
    \begin{itemize}
        \item \href{https://nvidia.connpass.com/event/39743/}{GTC Japan 2016 DLI in Hilton Tokyo Odaiba}
        \item \href{https://nvidia.connpass.com/event/54780/}{NVIDIA Deep Learning Institute 2017 in Tokyo Midtown and Takada-no-baba}
        \item \href{https://nvidia.connpass.com/event/68912/}{GTC Japan 2017 DLI in Hilton Tokyo Odaiba}
        \item \href{https://nvidia.connpass.com/event/189637/}{NVIDIA GTC 2020 DLI in Online}
        \item \href{https://nvidia.connpass.com/event/208506/}{NVIDIA GTC 2021 DLI in Online}
    \end{itemize}
    }

    % \emptySeparator
    % \researchexperience
    % {Jun. 2018}   {VALUENEX Japan Inc. | Part-time job{\normalfont  ~ [\href{https://en.valuenex.com/en/home}{\small{\websiteSymbol}}]}}{Tokyo, Japan}{Tokyo, Japan}
    % {Fab. 2016} {
    % Worked on dealing with large-scale nonstructural patent information in various forms, e.g., pre-processing, crawling, scraping, and analyzing these data.
    % }

    % \emptySeparator
    % \researchexperience
    % {}   {Works Applications Co., Ltd. | Software Intern{\normalfont  ~ [\href{https://www.worksap.com/}{\small{\websiteSymbol}}]}}{Tokyo, Japan}{Tokyo, Japan}
    % {Aug. 2015} {
    % Planned and implemented enterprise resource planning (ERP) packages.
    % }
\end{experiences}
